Molecular Analysis

### 2023-10-03 analysis/mol_analysis.Rmd
revise transmission chain plot

tnet_pl <- tnet %>%
  ggplot(aes(y = date_infection, x = virus, fill = virus, size = n)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  geom_point(shape = 21, color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
               arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "Number of infections", fill = "Virus") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  theme_custom() +
  theme(legend.position = "top",
        legend.direction = "horizontal",
        legend.box = "vertical",
        #plot.title.position = "plot",
        axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) +
  guides(fill = "none",
         size = guide_legend(nrow = 1, order = 1))

>>>>

tnet_pl <- tnet %>%
  ggplot(aes(y = date_infection, x = virus, fill = virus, size = n)) +
  facet_wrap(~ class, ncol = 2, scales = "free_x") +
  geom_point(shape = 21, color = "black") +
  geom_segment(aes(y = from, yend = to, xend = virus), size = 1,
               arrow = arrow(length = unit(0.2, "cm")), color = "black") +
  labs(size = "Number of infections", fill = "Virus") +
  coord_y_datetime(ylim = c(max(tnet$date_infection), min(tnet$date_infection))) +
  scale_y_datetime(date_breaks = "1 week", date_labels = "%b %d") +
  scale_size_discrete(range = c(4,8)) +
  scale_fill_manual(values = wes_palette("IsleofDogs1")) +
  theme_custom() +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        legend.box = "vertical",
        #plot.title.position = "plot",
        axis.title = element_blank(),
        #axis.text.x = element_blank(),
        #axis.ticks.x = element_blank(),
        panel.spacing = unit(1, "cm"),
        panel.grid.major.x = element_line(),
        panel.grid.minor.y = element_blank(),
        strip.text.x = element_text(size = 10, margin = margin(b = 10))) +
  guides(fill = "none",
         size = guide_legend(nrow = 1, order = 1))
